### 2018-03-12 paper/3-compute.tex
Rewrite the example with String keys

...
% \begin{figure}
% \begin{minted}{haskell}
% type Compute c k v = @\std{forall}@ f. c f => (k -> f v) -> k -> Maybe (f v)
% \end{minted}
% \caption{Compute abstractions}\label{fig-compute}
% \end{figure}
% Consider abstractions in Fig.~\ref{fig-compute}.

>>>>

We describe build tasks and their dependencies using functions of type
\hs{Compute}:

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
type Compute c k v = @\std{forall}@ f. c f => (k -> f v) -> k -> Maybe (f v)
\end{minted}
\vspace{1mm}

\noindent
A compute takes two arguments: \hs{fetch :: k -> f v} and \hs{key :: k}, and
returns either \hs{Nothing} to indicate that the \hs{key} is an input and hence
cannot be computed, or \hs{Just}~\hs{value} obtained by \hs{fetch}ing the
dependencies of the \hs{key} and performing the required computation. A compute
must be polymorphic in \hs{f} but may request certain computational
power\footnote{Readers familiar with \emph{lenses} or \emph{profunctor optics}
might recognise a familiar pattern. We discuss this in~\S\ref{sec-related}.} by
specifying the constraint~\hs{c}. Let us look at an example by recalling the
following spreadsheet from~\S\ref{sec-background-excel}:

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{bash}
A1 = 10
A2 = 20
B1 = A1 + A2
\end{minted}
\vspace{1mm}

\noindent
The only build task in this spreadsheet can be expressed as an \emph{applicative
compute}, operating on keys (cell names) of type \hs{String} and values of
type \hs{Integer}:

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
add :: Compute Applicative String Integer
add fetch key | key /= "B1" = Nothing
              | otherwise   = Just $ (+) <$> fetch "A1" <*> fetch "A2"
\end{minted}
\vspace{1mm}

\noindent
The cells \cmd{A1} and \cmd{A2} are inputs, which is indicated by returning
\hs{Nothing}. The cell \cmd{B1} is an output, whose value is computed by
fetching the values of \cmd{A1} and \cmd{A2} and applying the pure
function~\hs{(+)} using the methods of the \hs{Applicative} type
class~\cite{mcbride2008applicative}.

The \hs{Compute} type and the example above might seem mysterious. Why insist on
\hs{Compute} to be polymorphic in \hs{f}? Why choose the \hs{Applicative}
constraint?
